Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-10-31 paper/paper/SPIE/article.tex
wip - paper

\begin{table}[h!]
\small
\centering
\begin{tabular}{ c c c c c c c }
\hline
\textbf{ID}    & \textbf{Dimensions}  & \textbf{Voxel size (mm)} & \textbf{TR} & \textbf{Volumes} \\
\hline
PSYCH     & 128 x 128 x 70 & 1.5 x 1.5 x 1.5 & 3.0  & 300  \\
PARK      & 80 x 80 x 43   & 3.0 x 3.0 x 3.0 & 2.4  & 149  \\
OSTEO     & 64 x 64 x 36   & 3.4 x 3.4 x 3.0 & 2.5  & 300  \\
BILING    & 100 x 100 x 72 & 1.8 x 1.8 x 1.8 & 0.88 & 823  \\
LEARN     & 64 x 64 x 36   & 3.0 x 3.0 x 3.0 & 2.0  & 195  \\
DEPRESS   & 112 x 112 x 25 & 2.0 x 2.0 x 5.0 & 2.5 & 100   \\
AGING     & 74 x 74 x 32   & 3.0 x 3.0 x 4.0 & 2.0 & 300   \\
\hline
\end{tabular}
\caption{
    ID = Identifier for paper. TR = Time of Repetition (seconds).
    Time = total duration (minutes) of each scan. Dimensions listed as M x N x P,
    indicate P slices with dimensions M x N.
}
\label{table:1}
\end{table}

\begin{table}[h!]
\small
\centering
\begin{tabular}{ l l c c c }
\hline
\textbf{ID}  & \textbf{Subgroup / Condition}  & \textbf{Subjects}  & \textbf{Task} & \textbf{Scans per Subject} \\
\hline
PSYCH   &  high\_vigilance    & 12 / 11 & resting-state                    & 2 \\
        &  low\_vigilance     & 10 / 11 & resting-state                    & 2 \\
        &  trait\_attend      & 12 / 15 & resting-state                    & 2 \\
        &  trait\_non-attend  & 10 / 7  & resting-state                    & 2 \\
        &  task\_attend       & 13 / 15 & resting-state                    & 2 \\
        &  task\_nonattend    &  9 / 7  & resting-state                    & 2 \\
\hline
LEARN   &  task              & 24      & learn image sketches & 16 \\
        &  rest              & 24      & resting-state                    & 2 \\
\hline
REFLECT &  control (no pain) & 20      & resting-state                    & 1 \\
        &  duloxetine        & 19      & resting-state                    & 1 \\
        &  placebo           & 37      & resting-state                    & 1 \\
        &  allpain (duloxetine + placebo) & 56         & resting-state    & 1 \\
\hline
PARK    &  Parkinson's       & 17      & ANT                              & 6 \\
        &  control           & 17      & ANT                              & 6 \\
\hline
ECHO    &  summed/interleave & 31      & resting-state                    & 1 \\
        &  summed/interleave & 31      & imagery/reflection               & 4 \\
\hline
\end{tabular}
\caption{
    ID = Identifier for paper. FOV = Field of View. TR = Time of Repetition (seconds).
    Time = total duration (minutes) of each scan. Dimensions listed as M x N x P,
    indicate P slices with dimensions M x N.
}
\label{table:2}
\end{table}

>>>>

\begin{table}[h!]
\small
\centering
\begin{tabular}{ c c c c c c c }
\hline
\textbf{ID}    & \textbf{Dimensions}  & \textbf{Voxel size (mm)} & \textbf{TR} & \textbf{Volumes} & \textbf{n\_scans} \\
\hline
AGING     & 74 x 74 x 32   & 3.0 x 3.0 x 4.0 & 2.0  & 300 & 62  \\
BILING    & 100 x 100 x 72 & 1.8 x 1.8 x 1.8 & 0.88 & 823 & 90  \\
DEPRESS   & 112 x 112 x 25 & 2.0 x 2.0 x 5.0 & 2.5  & 100 & 72  \\
LEARN     & 64 x 64 x 36   & 3.0 x 3.0 x 3.0 & 2.0  & 195 & 432 \\
OSTEO     & 64 x 64 x 36   & 3.4 x 3.4 x 3.0 & 2.5  & 300 & 74  \\
PARK      & 80 x 80 x 43   & 3.0 x 3.0 x 3.0 & 2.4  & 149 & 552 \\
PSYCH     & 128 x 128 x 70 & 1.5 x 1.5 x 1.5 & 3.0  & 300 & 90  \\
\hline
\end{tabular}
\caption{
    ID = Identifier for paper. TR = Time of Repetition (seconds).
    Time = total duration (minutes) of each scan. Dimensions listed as M x N x P,
    indicate P horizontal / axial slices each with dimensions M x N.
}
\label{table:1}
\end{table}

\begin{table}[h!]
\small
\centering
\begin{tabular}{ l l c c c }
\hline
\textbf{ID}  & \textbf{Subgroup}  & \textbf{Subjects}  & \textbf{Task} & \textbf{Scans per Subject} \\
\hline
AGING   &  older             & 28      & resting-state         & 1 \\
        &  younger           & 34      & resting-state         & 1 \\
\hline
BILING  &  bilingual          & 59      & resting-state        & 1 \\
        &  monolingual        & 33      & resting-state        & 1 \\
\hline
DEPRESS &  depression         & 51      & resting-state        & 1 \\
        &  control            & 21      & resting-state        & 1 \\
\hline
LEARN   &  task              & 24      & learn image sketches  & 16 \\
        &  rest              & 24      & resting-state         & 2 \\
\hline
OSTEO   &  duloxetine        & 19      & taking duloxetine     & 1 \\
        &  pain              & 37      & placebo               & 1 \\
        &  nopain            & 20      & control               & 1 \\
\hline
PARK    &  Parkinson's       & 25      & ANT                   & 12 \\
        &  control           & 21      & ANT                   & 12 \\
\hline
PSYCH   &  vigilant           & 11     & resting-state        & 3 \\
        &  nonigilant         & 11     & resting-state        & 3 \\
        &  trait-attentive     & 11    & resting-state        & 3 \\
        &  trait-non-attentive & 11    & resting-state        & 3 \\
        &  task-attentive     & 11     & resting-state        & 3 \\
        &  task-nonattentive  & 11     & resting-state        & 3 \\
\hline
\end{tabular}
\caption{
    ID = Identifier for paper. FOV = Field of View. TR = Time of Repetition (seconds).
    Time = total duration (minutes) of each scan. Dimensions listed as M x N x P,
    indicate P slices with dimensions M x N.
}
\label{table:2}
\end{table}
